---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
```

```{css}
body {
  background-color: #E0E0E0;
}
```

## Pokemon data

The Pokemon data is collected from the most common answers to the daily [PokeDoku](https://pokedoku.com/) puzzles. PokeDoku is a puzzle game inspired by Sudoku where you have 9 tiles from a 3 by 3 square with various requirements. Each tile has 2 requirements a Pokemon must meet in order for the answer to be valid. Since multiple Pokemon can meet these requirements, a score is given based on how common your answer is on each tile.

I am analysing what types of Pokemon are the most common answers. I collect various information on the pokemon such as their name, the region they are from, the evolution form, their primary type and the base stat total (BST).

```{r}
library(tidyverse)
# Loading data
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRJiDFUifwlREs-W0UXsADT278joWTGYUNOgRm2v_yDLlsUQhjwwhdHQ6CUr3gCQBn3fh28i_SWSlz5/pub?output=csv")
latest_data <- logged_data %>% rename(name = 2, region = 3, evolution_form = 4, type = 5, BST = 6)

# Number of observations
observations = nrow(latest_data)

# Number of unique Pokemon listed
# Unique() function removes any duplicate data in an array/tibble. I learnt of this in STATS 326
unique_mons = latest_data %>% select(-Timestamp) %>% mutate(name = tolower(name)) %>% unique() %>% nrow()

# Mean BST
mean_BST = mean(latest_data$BST) %>% round()

```

Out of the `r observations` Pokemon recorded from the Google Form, there are `r unique_mons` unique Pokemon in the data collected. The mean base stat total of all Pokemon observed is `r mean_BST`.

```{r, fig.width = 15}
# Bar graph of frequency by primary type
ggplot(data = latest_data, mapping = aes(x = type, fill = evolution_form)) + geom_bar() + theme_minimal() +
  theme(plot.background = element_rect(fill = "#E0E0E0"), panel.background = element_rect(fill = "white")) +
  labs(title = "Primary Type Bar Graph",
       x = "Primary Type",
       fill = "Evolution form")

```


```{r}
# Bar graph of frequency by region
ggplot(data = latest_data, mapping = aes(x = region)) + geom_bar() + theme_minimal() +
  labs(title = "Region Bar Graph",
       subtitle = "The number of Pokemon recorded in each region",
       x = "Region")
```

```{r}
# finds the current strongest Pokemon
# the which.max gives the index of the largest element in an array. I learnt of this in STATS 326
strongest_pokemon = latest_data[which.max(latest_data$BST),]

# finds the current weakest Pokemon
# the which.min gives the index of the smallest element in an array. I learnt of this in STATS 326
weakest_pokemon = latest_data[which.min(latest_data$BST),]
```

`r strongest_pokemon$name` is the strongest recorded Pokemon with a base stat total of `r strongest_pokemon$BST` and has a primary type of `r strongest_pokemon$type`. They are from the `r strongest_pokemon$region` region. More info on `r strongest_pokemon$name` can be found [here][url_strongest].

`r weakest_pokemon$name` is the weakest recorded Pokemon with a base stat total of `r weakest_pokemon$BST` and has a primary type of `r weakest_pokemon$type`. They are from the `r weakest_pokemon$region` region. More info on `r weakest_pokemon$name` can be found [here][url_weakest].

[url_strongest]: https://pokemondb.net/pokedex/`r tolower(strongest_pokemon$name)`
[url_weakest]: https://pokemondb.net/pokedex/`r tolower(weakest_pokemon$name)`
