---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
```

```{css}
@import url('https://fonts.googleapis.com/css2?family=Funnel+Sans:ital,wght@0,300..800;1,300..800&family=Google+Sans:ital,opsz,wght@0,17..18,400..700;1,17..18,400..700&display=swap');
body {
  background-color: #E0E0E0;
  font-family: "Funnel Sans"
}
```

## Pokemon data

The Pokemon data is collected from the most common answers to the daily [PokeDoku](https://pokedoku.com/) puzzles. PokeDoku is a puzzle game inspired by Sudoku where you have 9 tiles from a 3 by 3 square with various requirements. Each tile has 2 requirements a Pokemon must meet in order for the answer to be valid. Since multiple Pokemon can meet these requirements, a score is given based on how common your answer is on each tile.

I am analysing what types of Pokemon are the most common answers. I collect various information on the pokemon such as their name, the region they are from, the evolution form, their primary type and the base stat total (BST).

```{r}
library(tidyverse)
# Loading data
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRJiDFUifwlREs-W0UXsADT278joWTGYUNOgRm2v_yDLlsUQhjwwhdHQ6CUr3gCQBn3fh28i_SWSlz5/pub?output=csv")
latest_data <- logged_data %>% rename(name = 2, region = 3, evolution_form = 4, type = 5, BST = 6)
# Number of unique Pokemon listed
unique_mons = latest_data %>% select(-Timestamp) %>% mutate(name = tolower(name)) %>% unique() %>% nrow()

# Finds the most common region answered and how many of said region
region_table = table(latest_data$region)
common_region = names(region_table)[which.max(region_table)]

# Finds the current strongest pokemon
strongest_pokemon = latest_data[which.max(latest_data$BST),]

```

`r max(region_table)` Pokemon were from the `r common_region` region, which was the region with the most 
Pokemon from the data collected. There are `r unique_mons` unique Pokemon in the data collected.

```{r, fig.width = 15}
# Bar graph of frequency by primary type
ggplot(data = latest_data, mapping = aes(x = type, fill = evolution_form)) + geom_bar() + theme_minimal() +
  theme(plot.background = element_rect(fill = "#E0E0E0"), panel.background = element_rect(fill = "white")) +
  labs(title = "Primary Type Bar Graph",
       x = "Primary Type",
       fill = "Evolution form")

# Most common primary type
type_table = table(latest_data$type)
common_type = names(type_table)[which.max(type_table)]
```

The most common primary type was `r common_type` with `r max(type_table)` Pokemon having it as their primary type.

```{r, fig.width = 15}
# Calculating summary data by grouping by type and plotting the average BST by type
mean_BST_by_type = latest_data %>% group_by(type) %>% summarise(mean = mean(BST), n = n())
ggplot(data = mean_BST_by_type) + geom_col(aes(x = type, y = mean)) + theme_minimal() + 
  theme(plot.background = element_rect(fill = "#E0E0E0"), panel.background = element_rect(fill = "white")) +
  labs(title = "Average BST by type", 
       subtitle = "Comparing the average Base Stat Total by the Pokemon's type",
       x = "Primary Type",
       y = "Average BST")
```

`r strongest_pokemon$name` is the strongest recorded Pokemon with a base stat total of `r strongest_pokemon$BST` and has a primary type of `r strongest_pokemon$type`. They are from the `r strongest_pokemon$region` region. More info on `r strongest_pokemon$name` can be found [here][url].

[url]: https://pokemondb.net/pokedex/`r tolower(strongest_pokemon$name)`
